\textls[-0]{\thetitle}

### 2022-11-11 agda-files.tex
Update Instruction in Appendix.

We suggest using editors with proper syntax highlighting, e.g. VSCode with agda-code plugins, to read these source files.

>>>>

We suggest using editors with proper syntax highlighting to read these source files. e.g. VSCode with \textit{language-agda} plugin.\footnote{\url{https://marketplace.visualstudio.com/items?itemName=j-mueller.agda}}
